Maenpuen *et al.* --American Journal of Botany-- Appendix S1

### 2022-06-20 ms/LMA_method.Rmd
update refs

Data and codes for this manuscript are archived on Zenodo at https://doi.org/10.5281/zenodo.6665083 and also available on Github at https://github.com/mattocci27/leaf-disc.

>>>>

Data, codes and computing environments to reproduce this manuscript are archived on Zenodo at https://doi.org/10.5281/zenodo.6665083 and also available on Github at https://github.com/mattocci27/leaf-disc.

### 2022-06-20 ms/LMA_method.tex
update refs

Data and codes for this manuscript are archived on Zenodo at \url{https://doi.org/10.5281/zenodo.6665083} and also available on Github at \url{https://github.com/mattocci27/leaf-disc}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Yang2020}{}}%
Yang, J., J. Lu, Y. Chen, E. Yan, J. Hu, X. Wang, and G. Shen. 2020. \href{https://doi.org/10.3389/fpls.2020.00053}{Large {Underestimation} of {Intraspecific Trait Variation} and {Its Improvements}}. \emph{Frontiers in Plant Science} 11: 53.

@@

\textbf{Fig. 3.}
Relationships between petiole to leaf dry mass ratio and (a) leaf area and (b) whole-leaf to leaf disc LMA ratio.
Blue solid lines indicate ordinary least squares (OLS) regressions.
The 95\% confidence intervals are presented as the shaded area.
All the correlations are significant (P \textless{} 0.001).
All the samples were obtained with a diameter 1.0-cm leaf punch.

>>>>

Data, codes and computing environments to reproduce this manuscript are archived on Zenodo at \url{https://doi.org/10.5281/zenodo.6665083} and also available on Github at \url{https://github.com/mattocci27/leaf-disc}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Yang2020}{}}%
Yang, J., J. Lu, Y. Chen, E. Yan, J. Hu, X. Wang, and G. Shen. 2020. \href{https://doi.org/10.3389/fpls.2020.00053}{Large underestimation of intraspecific trait variation and its improvements}. \emph{Frontiers in Plant Science} 11: 53.

@@

\textbf{Fig. 3.}
Relationships between petiole to leaf dry mass ratio and (a) leaf area and (b) whole-leaf to leaf disc LMA ratio.
Blue solid lines indicate ordinary least squares (OLS) regressions.
The 95\% confidence intervals are presented as the shaded area.
All the correlations are significant (P \textless{} 0.001).
Note that all the samples were obtained with a diameter 1.0-cm leaf punch.
